Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

\begin{theorem} \label{thm:main-recur}
    Equipped with the algorithm $\A$ as described above, the $k$-SJ problem with $k \ge 3$ can be solved in time
    \myeqn{
        O(k^3) \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big)
        %\nn
        \label{eqn:main:reccurrence}
    }
    where $n$ (resp., $\out$) is the input (resp., output) size of the problem.
%     time using $O(n + \out)$ space, plus the worst-case space of $\A$ on any $(k-1)$-SJ instance with input size $n$ and output size $\out$.
\end{theorem}

@@

\begin{theorem} \label{thm:main-alg}
    For $k \ge 3$, we can settle $k$-SJ with a comparison-based algorithm in $O( c^k (k!)^3 \cdot (n \log n + k \cdot \out))$ time.
    %and $O(k \cdot n + \out)$ space, where $c > 1$ is a positive constant.
\end{theorem}

@@

\input{thm1.2}

>>>>

\begin{theorem} \label{thm:main-recur}
    Equipped with the algorithm $\A$ as described above, the $k$-SJ problem with $k \ge 3$ can be solved in time
    \myeqn{
        O(k^3) \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big)
        %\nn
        \label{eqn:main:reccurrence}
    }
    where $n$ (resp., $\out$) is the input (resp., output) size of the problem. Furthermore, if $\A$ is comparison-based, so is the $k$-SJ algorithm.

%     time using $O(n + \out)$ space, plus the worst-case space of $\A$ on any $(k-1)$-SJ instance with input size $n$ and output size $\out$.
\end{theorem}

@@

\begin{theorem} \label{thm:main-alg}
    For $k \ge 3$, we can settle $k$-SJ with a comparison-based algorithm in $O( c^{k-1} (k!)^3 \cdot (n \log n + k \cdot \out))$ time.
    %and $O(k \cdot n + \out)$ space, where $c > 1$ is a positive constant.
\end{theorem}

@@

As mentioned in Section~\ref{sec:intro:prev}, 2-SJ can be solved in $F_2(n, \out) = O(n \log n + \out)$ time using a comparison-based algorithm. By Theorem~\ref{thm:main-recur}, in general, a comparison-based $(k-1)$-SJ algorithm with runtime $F_{k-1}(n, \out)$ spawns a comparison-based $k$-SJ algorithm whose running time $F_k(n, \out)$ obeys \eqref{eqn:main:reccurrence}. Specifically, for $k \ge 3$, there is a constant $c > 1$ such that
\myeqn{
    && F_{k}(n, \out) \nn \\
    &\le& c \cdot k^3 \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big) \nn \\
    &=& c^2 \cdot k^3(k-1)^3 \cdot (F_{k-2}(n,\out) + n\log n + k\cdot \out) + \nn \\
    && c \cdot k^3(n\log n + k\cdot \out ) \nn\\
    &<& c^2 \cdot k^3(k-1)^3 \cdot F_{k-2}(n,\out) +  \nn\\
    && (c+c^2)\cdot k^3(k-1)^3(n\log n + k \cdot\out) \nn \\
    &\leq& c^3 \cdot k^3(k-1)^3(k-2)^3 \cdot F_{k-3}(n,\out) + \nn\\
    && (c+c^2+c^3)\cdot k^3(k-1)^3(k-2)^3(n\log n + k \cdot\out) \nn\\
    &\leq& ... \nn \\
    &\leq& c^{k-2} \cdot (k!)^3 \cdot F_{2}(n,\out) + \nn \\
    && \Big(\sum_{i =1}^{k-2}c^i \Big)\cdot (k!)^3\cdot (n\log n + k \cdot\out) \nn \\
    &\leq & 2c^{k-1} \cdot (k!)^3 \cdot O(n\log n + k \cdot\out) \nn
}
which completes the proof of Theorem~\ref{thm:main-alg}.
